\forestclaw: Hybrid forest-of-octrees AMR for hyperbolic conservation laws

### 2013-03-16 docs/parco13/abstract.tex
Update ccgo bib file

To enable hardware acceleration for parallel dynamic AMR, we like to
build upon the forest-of-octrees paradigm because of its low overhead
and proven scalability \cite{BursteddeWilcoxGhattas11}.  This approach
identifies each octree leaf with a mesh element.  In our work, we go
beyond the traditional high-order element and define each element to
be a dense compute patch with $m^d$ DOFs.  In fact, this approach
resembles block-structured AMR \cite{be-ol:1984, be-co:1989, be-le:1991,
ColellaGravesKeenEtAl07,Uintah} except that the
patches are not overlapping, which enables us to capitalize on our
previous experience with scalable FE solvers for PDEs
\cite{BursteddeStadlerAlisicEtAl13}.  The Clawpack software
\cite{LeVeque97} provides a popular implementation of such a patch.
It has been designed to solve hyperbolic conservation laws
% on a uniform compute patch
and successfully used in the context of block-structured AMR
\cite{be-le:1991, amrclaw}.

>>>>

To enable hardware acceleration for parallel dynamic AMR, we like to
build upon the forest-of-octrees paradigm because of its low overhead
and proven scalability \cite{BursteddeWilcoxGhattas11}.  This approach
identifies each octree leaf with a mesh element.  In our work, we go
beyond the traditional high-order element and define each element to
be a dense compute patch with $m^d$ DOFs.  In fact, this approach
resembles block-structured AMR \cite{be-ol:1984, be-co:1989, be-le:1991,
ColellaGravesKeenEtAl07,
BerzinsLuitjensMengEtAl10} except that the
patches are not overlapping, which enables us to capitalize on our
previous experience with scalable FE solvers for PDEs
\cite{BursteddeStadlerAlisicEtAl13}.  The Clawpack software
\cite{LeVeque97} provides a popular implementation of such a patch.
It has been designed to solve hyperbolic conservation laws
% on a uniform compute patch
and successfully used in the context of block-structured AMR
\cite{be-le:1991, amrclaw}.
